---
title: "Introduction to graphdata"
author: "Matthias Ronnau"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to graphdata}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(graphdata)
```

### Generating graph data

The package "`graphdata`" is a simple package that transforms purchase data
into an iGraph object. The iGraph package is useful for visualizing and
computing various statistics about a social network, but sometime data must
be transformed in order to work properly. This package takes event level
data and transforms it into a network that is workable with iGraph.


### Generating the `iGraph` object

The dataframe must have a unique identifier to group by, such as a user id. 
It must also have a unique identifier for every product in the network, 
such as a product id.

```{r}
set.seed(277)
df <- data.frame("user_identifier" = rep(1:3, 3), 
                 "product" = 277:285, 
                 "price" = c(sample(1:500, 4, replace = TRUE), NA, 
                             sample(1:500, 4, replace = TRUE)))
```

The data to be used must be cleansed of all missing values.

```{r}
cleaned_df <- na.omit(df)
```

The cleaned data can now be transformed into an iGraph object with `graph_data()`.

```{r}
g <- graph_data(data = cleaned_df, id = "user_identifier", 
                product_id = "product")
g
```

The resulting object can now be visualized as a network or transformed into a 
dataframe using built in iGraph functions in order to compute various 
statistics about the network.
